Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-25 netsoft_paper.tex
the fourth version

\begin{table}[!t]
\caption{40 POPULAR APPLICATIONS’ AVERAGE F1 SCORE IN 10 ROUNDS}
\label{table:classification_result}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
Application name    & Average F1 score    & Application name  & Average F1 score   \\ \hline
OneDrive            & 0.991255            & Trello            & 0.988889           \\ \hline
gamerAnimad         & 0.985714            & Dropbox           & 0.985714           \\ \hline
AmazonMusi          & 0.977461            & MEGAsync          & 0.968889           \\ \hline
MEGAsync            & 0.968889            & BattleNet         & 0.967812           \\  \hline
Udacity             & 0.966667            & Lity              & 0.966427            \\ \hline
Tumblr              & 0.964624            & Asana             & 0.963492            \\ \hline
Skype               & 0.963117            & Twitch            & 0.963117            \\ \hline
TeamViewer          & 0.946667            & FileZilla         & 0.946429            \\ \hline
Agoda               & 0.944764            & TripAdvisor       & 0.942075            \\  \hline
Pinterest           & 0.936026            & BBCNews           & 0.931049            \\  \hline
LINE                & 0.923904            & Slack             & 0.920985            \\ \hline
Twitter             & 0.917906            & Youku             & 0.913925            \\ \hline
Evernote            & 0.912381            & Snapchat          & 0.912221            \\ \hline
Weibo               & 0.910872            & WeChat            & 0.906349            \\ \hline
GoogleDrive         & 0.896612            & Trivago           & 0.895406             \\ \hline
iTunes              & 0.890464            & Netflix           & 0.876234             \\ \hline
Facebook            & 0.868641            & Telegram          & 0.862222             \\ \hline
Airbnb              & 0.857029            & Spotify           & 0.856971             \\ \hline
Instagram           & 0.833465            & TED               & 0.829277             \\ \hline
Tmall               & 0.799747            & YouTube           & 0.713084             \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[!t]
\caption{40 POPULAR APPLICATIONS’ AVERAGE \\ F1 SCORE IN 10 ROUNDS}
\label{table:classification_result}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
Application name    & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}    & Application name  & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}   \\ \hline
OneDrive            & 0.991255            & Trello            & 0.988889           \\ \hline
gamerAnimad         & 0.985714            & Dropbox           & 0.985714           \\ \hline
AmazonMusi          & 0.977461            & MEGAsync          & 0.968889           \\ \hline
MEGAsync            & 0.968889            & BattleNet         & 0.967812           \\  \hline
Udacity             & 0.966667            & Lity              & 0.966427            \\ \hline
Tumblr              & 0.964624            & Asana             & 0.963492            \\ \hline
Skype               & 0.963117            & Twitch            & 0.963117            \\ \hline
TeamViewer          & 0.946667            & FileZilla         & 0.946429            \\ \hline
Agoda               & 0.944764            & TripAdvisor       & 0.942075            \\  \hline
Pinterest           & 0.936026            & BBCNews           & 0.931049            \\  \hline
LINE                & 0.923904            & Slack             & 0.920985            \\ \hline
Twitter             & 0.917906            & Youku             & 0.913925            \\ \hline
Evernote            & 0.912381            & Snapchat          & 0.912221            \\ \hline
Weibo               & 0.910872            & WeChat            & 0.906349            \\ \hline
GoogleDrive         & 0.896612            & Trivago           & 0.895406             \\ \hline
iTunes              & 0.890464            & Netflix           & 0.876234             \\ \hline
Facebook            & 0.868641            & Telegram          & 0.862222             \\ \hline
Airbnb              & 0.857029            & Spotify           & 0.856971             \\ \hline
Instagram           & 0.833465            & TED               & 0.829277             \\ \hline
Tmall               & 0.799747            & YouTube           & 0.713084             \\ \hline
\end{tabular}
\end{table}
